% ============================================
% 摘要
% ============================================
\setcounter{page}{1}
\pagenumbering{Roman}

\section*{摘\quad 要}
\addcontentsline{toc}{section}{摘要}

随着互联网技术的快速发展，在线问卷调查已成为数据收集的重要手段。然而，现有问卷平台在协作编辑、智能化分析等方面仍存在不足。本文设计并实现了一个基于 Next.js 的在线问卷系统，旨在提供一个功能完善、易于协作、具备智能化分析能力的问卷平台。

系统采用 Next.js 全栈框架，结合 React、TypeScript、Tailwind CSS 构建前端界面，使用 Prisma ORM 和 PostgreSQL 进行数据持久化。系统支持多种题型（单选、多选、矩阵、评分、NPS 等共 18 种），提供可视化问卷编辑器、版本管理、数据可视化统计等功能。在创新性方面，系统集成了 DeepSeek AI 实现问卷智能生成与数据分析总结，并基于 Pusher 实现了多人实时协作编辑功能。

本文详细阐述了系统的需求分析、架构设计、数据库设计、核心模块实现以及测试验证过程。实验结果表明，系统运行稳定，功能完整，能够满足在线问卷调查的各项需求。

\vspace{1em}
\noindent\textbf{关键词：}在线问卷系统；Next.js；人工智能；实时协作；数据可视化

\newpage

% ---------- 英文摘要 ----------
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

With the rapid development of Internet technology, online survey has become an important means of data collection. However, existing survey platforms still have shortcomings in collaborative editing and intelligent analysis. This paper designs and implements an online survey system based on Next.js, aiming to provide a fully functional, easy-to-collaborate, and intelligently analyzable survey platform.

The system adopts the Next.js full-stack framework, combining React, TypeScript, and Tailwind CSS to build the front-end interface, and uses Prisma ORM and PostgreSQL for data persistence. The system supports multiple question types (single choice, multiple choice, matrix, rating, NPS, etc., totaling 18 types), providing a visual questionnaire editor, version management, and data visualization statistics. In terms of innovation, the system integrates DeepSeek AI to achieve intelligent questionnaire generation and data analysis summarization, and implements multi-user real-time collaborative editing based on Pusher.

This paper elaborates on the system's requirements analysis, architecture design, database design, core module implementation, and testing verification process. Experimental results show that the system runs stably, has complete functions, and can meet the various needs of online survey.

\vspace{1em}
\noindent\textbf{Keywords:} Online Survey System; Next.js; Artificial Intelligence; Real-time Collaboration; Data Visualization

\newpage
